Displacement of fishing effort by Large Scale Marine Protected Areas[^*]

### 2018-10-20 docs/Manuscript.tex
Slight changes to manuscript, major results coming

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{\label{fig:unnamed-chunk-3}\label{fig:LSMPAs_map}Large Scale Marine
Protected Areas. The map shows all areas larger than 250,000
Km\textsuperscript{2}. Areas in dark blue meet at least one of these
conditions: reported no take area is greater than 0, are categorized as
IUCN Ia or Ib, their designated english name is `Protected Area'.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{\label{fig:unnamed-chunk-4}\label{fig:PNA_map}Map of the Exclusive
Economic Zones (EEZs) of the region of interest. A solid line indicates
countries that belong to the PNA, while a dashed line indicates all
others. A red line indicates the Kiribati EEZ, and a solid red polygon
delineates PIPA.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-7}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Group & n & Before & After & Change (A / B)\\
\midrule
Control & 26 & 11.74 & 20.13 & 1.72\\
Treatment & 61 & 10.67 & 18.36 & 1.72\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{\label{fig:unnamed-chunk-8}\label{fig:all_vessels}Fishing hours and
number of vessels by month for all vessels. Vertical dashed lines
indicates dates when satellites were added, solid line indicates PIPA
closurePIPA closure.}
\end{figure}

@@

Our second part of the analyses focuses on the redistribution of fishing
effort. In other words, identifying where do vessels that used to fish
inside PIPA go after its establishment.

Furthermore, the presence and reaction of other vessels may in turn
affect a fishers decission making process, seeking to avoid crowded
areas. Additionally, if fishers show high site fidelity or their ability
to fish is highly linkted to a few spatial portions, there might be an
associated cost of learning to identify new suitable fishing grounds.
For example, \citet{elahi_2018} showed that redistributed effort was
higher along the borders of the closure, indicative of a possible
habitat-dependency.

However, the role of institutions must also be considered. The spatial
closure described by \citet{elahi_2018} occured within an EEZ. As stated
before LSMPAs, often span the entirety of an EEZ. In the case of purse
seining in the PNA, vessels purchase access to the fishery at the
beginning of the season. If a vessel decides to fish within the PNA,
they've already made the decission to pay for access, expecting higher
returns from fishing there than in the High Seas. In the particular case
of PIPA, one would expect that a vessel holding a permit to fish in
I-Kiribati waters would then move to other fishing grounds within
Kiribati after the closure. Alternatively, if a vessel fishes illegaly
in I-Kiribati waters before the implementation, one would expect them to
reallocate to other where probability of being caught is equal or lower.
In this case, they might then choose to move to other I-Kiribati waters,
waters of countries that have similar enforcement levels, or the High
Seas.

@@

\caption{\label{tab:unnamed-chunk-10}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
\centering
\begin{tabular}[t]{lr}
\toprule
country & change\\
\midrule
EEZ COK 1 & 0.53\\
EEZ FSM 1 & 0.81\\
EEZ KIR 1 & -0.16\\
EEZ KIR 2 & 4.50\\
EEZ KIR 3 & -2.79\\
\addlinespace
EEZ MHL 1 & -0.44\\
EEZ NRU 1 & 0.07\\
EEZ PNG 2 & -9.07\\
EEZ SLB 1 & 3.18\\
EEZ TUV 1 & 1.27\\
\addlinespace
HS & 3.93\\
HS COK 1 & 0.06\\
HS KIR 1 & 2.96\\
HS KIR 2 & 1.07\\
HS KIR 3 & 2.53\\
PIPA PIPA 1 & -8.25\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
\caption{\label{fig:unnamed-chunk-11}\label{fig:all_vessels}Daily fishing
hours for all vessels in our main treatment-control groups. Solid
straight lines show a linear trend by period (pre-psot) and treatment.
The other red and blue lines show monthly avarages. Vertical dashed line
indicates PIPA closure.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{\label{fig:unnamed-chunk-13}\label{fig:long}Coefficient estimates
for each model. Top pannel indicates variable, x-axis represents model
specification, and y-axis coefficient estimate.}
\end{figure}

Recall that to evaluate the redistribution of fishing effort we only
track fishing vessels that belong to the treated group. In this case, we
calculate the proportion of fishing effort allocated every month to each
spatially explicit region outlined by EEZs and the high seas. For purse
seiners, these represent 9 main EEZs, PIPA, the high seas, and a group
of other EEZs. Figure \ref{fig:redist_trend_ps} shows the monthly
relative fishing hours that each region received by all 61 treated
vessels. The top-left panel shows the change in fishing effort inside
PIPA, including the preemptive fishing and immediate reduction
previously reported \citep{mcdermott_2018}.

The change in the relative allocation of fishing effort by purse seiners
increases in eight of the 12 regions after PIPA implementation (Table
\ref{tab:disp_mod}). The largest increase is observed for the I-Kiribati
EEZ, with an average increase of 0.11 (\emph{p \textless{} 0.001}). In
other words, the redistribution of treated vessels caused a 10\%
increase in the \emph{relative} allocation of fishing effort within
I-Kiribati waters. The only decrease is observed for Papua New Guinea,
but the coefficient is not significant. Figure \ref{fig:map_change_ps}
provides a spatial representation of these changes. It is evident that
the increase in relative fishing effort is greater for for regions
closer to PIPA.

\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
\caption{\label{fig:unnamed-chunk-15}\label{fig:redist_trend_ps}Monthly
relative allocation of fishing effort by PIPA-fishing vessels before and
after PIPA for 9 EEZs, PIPA, the high seas and `other EEZs'.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-16-1.pdf}
\caption{\label{fig:unnamed-chunk-16}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for purse seiners.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-17}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)}
\centering
\begin{tabular}[t]{ll}
\toprule
term & h\_prop\\
\midrule
(Intercept) & 0.087 (0.002)***\\
post & -0.081 (0.003)***\\
sate2 & -0.003 (0.001)***\\
sate3 & -0.002 (0.001)\\
post:countryEEZ COK 1 & 0.088 (0.002)***\\
\addlinespace
post:countryEEZ FSM 1 & 0.091 (0.003)***\\
post:countryEEZ KIR 1 & 0.081 (0.003)***\\
post:countryEEZ KIR 2 & 0.127 (0.004)***\\
post:countryEEZ KIR 3 & 0.055 (0.005)***\\
post:countryEEZ MHL 1 & 0.078 (0.003)***\\
\addlinespace
post:countryEEZ NRU 1 & 0.083 (0.003)***\\
post:countryEEZ PNG 2 & -0.008 (0.005)*\\
post:countryEEZ SLB 1 & 0.114 (0.004)***\\
post:countryEEZ TUV 1 & 0.095 (0.003)***\\
post:countryHS & 0.122 (0.003)***\\
\addlinespace
post:countryHS COK 1 & 0.083 (0.002)***\\
post:countryHS KIR 1 & 0.112 (0.003)***\\
post:countryHS KIR 2 & 0.093 (0.002)***\\
post:countryHS KIR 3 & 0.108 (0.003)***\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
\caption{\label{fig:unnamed-chunk-18}\label{fig:baci_strict}Stream of
fishing events by vessels through time. Each line represents a vessel,
with dots indicating months with fishing activity and colors indicating
the pre and post periods.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
\caption{\label{fig:unnamed-chunk-21}\label{fig:q1}Interaction of quarters
and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
\caption{\label{fig:unnamed-chunk-22}\label{fig:q2}Interaction of quarters
and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
\caption{\label{fig:unnamed-chunk-23}\label{fig:q3}Interaction of quarters
and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
\caption{\label{fig:unnamed-chunk-24}\label{fig:q4}Interaction of quarters
and treatment. Control group is japanese vessels.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
\caption{\label{fig:unnamed-chunk-25}\label{fig:ym1}Interaction of
year-month and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
\caption{\label{fig:unnamed-chunk-26}\label{fig:ym2}Interaction of
year-month and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
\caption{\label{fig:unnamed-chunk-27}\label{fig:ym3}Interaction of
year-month and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-28-1.pdf}
\caption{\label{fig:unnamed-chunk-28}\label{fig:ym4}Interaction of
year-month and treatment. Control group is japanese vessels.}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}Large Scale Marine
Protected Areas. The map shows all areas larger than 250,000
Km\textsuperscript{2}. Areas in dark blue meet at least one of these
conditions: reported no take area is greater than 0, are categorized as
IUCN Ia or Ib, their designated english name is `Protected Area'.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{\label{fig:unnamed-chunk-3}\label{fig:PNA_map}Map of the Exclusive
Economic Zones (EEZs) of the region of interest. A solid line indicates
countries that belong to the PNA, while a dashed line indicates all
others. A red line indicates the Kiribati EEZ, and a solid red polygon
delineates PIPA.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_n_s}Number of fishing vessels and mean daily fishing hours by group before and after PIPA implementation.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Group & n & Before & After & Change (A / B)\\
\midrule
Control & 26 & 11.74 & 20.13 & 1.72\\
Treatment & 61 & 10.67 & 18.36 & 1.72\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-7-1.pdf}
\caption{\label{fig:unnamed-chunk-7}\label{fig:all_vessels}Fishing hours and
number of vessels by month for all vessels. Vertical dashed lines
indicates dates when satellites were added, solid line indicates PIPA
closurePIPA closure.}
\end{figure}

@@

Our second part of the analyses focuses on the redistribution of fishing
effort. The role of institutions may play an important role. As stated
before, LSMPAs often span the entirety of an EEZ. In the case of purse
seining in the PNA, vessels purchase access to the fishery at the
beginning of the season. If a vessel decides to fish within the PNA,
they've already made the decission to pay for access, expecting higher
returns from fishing there than in the High Seas. In the particular case
of PIPA, one would expect that a vessel holding a permit to fish in
I-Kiribati waters would then move to other fishing grounds within
Kiribati after the closure. Alternatively, if a vessel fishes illegaly
in I-Kiribati waters before the implementation, one would expect them to
reallocate to other regions with equal or less enforcement. In this
case, they might then choose to move to other I-Kiribati waters, waters
of countries that have similar enforcement levels, or the High Seas.

@@

\caption{\label{tab:unnamed-chunk-9}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
\centering
\begin{tabular}[t]{lr}
\toprule
country & change\\
\midrule
EEZ COK 1 & 0.53\\
EEZ FSM 1 & 0.81\\
EEZ KIR 1 & -0.16\\
EEZ KIR 2 & 4.50\\
EEZ KIR 3 & -2.79\\
\addlinespace
EEZ MHL 1 & -0.44\\
EEZ NRU 1 & 0.07\\
EEZ PNG 2 & -9.07\\
EEZ SLB 1 & 3.18\\
EEZ TUV 1 & 1.27\\
\addlinespace
HS & 3.93\\
HS COK 1 & 0.06\\
HS KIR 1 & 2.96\\
HS KIR 2 & 1.07\\
HS KIR 3 & 2.53\\
PIPA PIPA 1 & -8.25\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Daily fishing
hours for all vessels in our main treatment-control groups. Solid
straight lines show a linear trend by period (pre-psot) and treatment.
The other red and blue lines show monthly avarages. Vertical dashed line
indicates PIPA closure.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-12-1.pdf}
\caption{\label{fig:unnamed-chunk-12}\label{fig:long}Coefficient estimates
for each model. Top pannel indicates variable, x-axis represents model
specification, and y-axis coefficient estimate.}
\end{figure}

Recall that to evaluate the redistribution of fishing effort we only
track fishing vessels that belong to the treated group. Figure
\ref{fig:fishing_raster} provides a spatial representation of these
changes. Note that 2013 effort distribution is roughly similar across
vessels. Then in 2014 there is a sharp increase in fishing hours by
treated vessels inside PIPA (blue paradox). In 2015 treated vessels then
allocate more effort to the easternmost Kiribati EEZ (see Figure
\label{fig:PNA_map}) and the high seas. In 2016 spatial distribution of
fishing effort is again similar across groups. It is evident that the
increase in relative fishing effort is greater for for regions closer to
PIPA, and.

Four our empirical identification we calculated the proportion of
fishing effort allocated every month to each spatially explicit regions
defined in section \ref{methods}. For purse seiners, these represent 9
main EEZs, PIPA, the high seas, and a group of other EEZs. Figure
\ref{fig:redist_trend_ps} shows the monthly relative fishing hours that
each region received by all 61 treated vessels. The top-left panel shows
the change in fishing effort inside PIPA, including the preemptive
fishing and immediate reduction previously reported
\citep{mcdermott_2018}. The change in the relative allocation of fishing
effort by purse seiners increases in eight of the 12 regions after PIPA
implementation (Table \ref{tab:disp_mod}, fig:map\_change\_ps). The
largest increase is observed for the I-Kiribati EEZ, with an average
increase of 0.11 (\emph{p \textless{} 0.001}). In other words, the
redistribution of treated vessels caused a 10\% increase in the
\emph{relative} allocation of fishing effort within I-Kiribati waters.
The only decrease is observed for Papua New Guinea, but the coefficient
is not significant.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{\label{fig:unnamed-chunk-13}\label{fig:fishing_raster}Yearly
spatial distribution of fishing effort by treated and control vessels.
Colors have been adjusted relative to the maximum observed by group and
year.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
\caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend_ps}Monthly
relative allocation of fishing effort by PIPA-fishing vessels before and
after PIPA for 9 EEZs, PIPA, the high seas and `other EEZs'.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
\caption{\label{fig:unnamed-chunk-15}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for purse seiners.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-16}\label{tab:disp_mod}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)}
\centering
\begin{tabular}[t]{ll}
\toprule
term & h\_prop\\
\midrule
(Intercept) & 0.087 (0.002)***\\
post & -0.081 (0.003)***\\
sate2 & -0.003 (0.001)***\\
sate3 & -0.002 (0.001)\\
post:countryEEZ COK 1 & 0.088 (0.002)***\\
\addlinespace
post:countryEEZ FSM 1 & 0.091 (0.003)***\\
post:countryEEZ KIR 1 & 0.081 (0.003)***\\
post:countryEEZ KIR 2 & 0.127 (0.004)***\\
post:countryEEZ KIR 3 & 0.055 (0.005)***\\
post:countryEEZ MHL 1 & 0.078 (0.003)***\\
\addlinespace
post:countryEEZ NRU 1 & 0.083 (0.003)***\\
post:countryEEZ PNG 2 & -0.008 (0.005)*\\
post:countryEEZ SLB 1 & 0.114 (0.004)***\\
post:countryEEZ TUV 1 & 0.095 (0.003)***\\
post:countryHS & 0.122 (0.003)***\\
\addlinespace
post:countryHS COK 1 & 0.083 (0.002)***\\
post:countryHS KIR 1 & 0.112 (0.003)***\\
post:countryHS KIR 2 & 0.093 (0.002)***\\
post:countryHS KIR 3 & 0.108 (0.003)***\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
\caption{\label{fig:unnamed-chunk-17}\label{fig:baci_strict}Stream of
fishing events by vessels through time. Each line represents a vessel,
with dots indicating months with fishing activity and colors indicating
the pre and post periods.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
\caption{\label{fig:unnamed-chunk-20}\label{fig:q1}Interaction of quarters
and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-21-1.pdf}
\caption{\label{fig:unnamed-chunk-21}\label{fig:q2}Interaction of quarters
and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-22-1.pdf}
\caption{\label{fig:unnamed-chunk-22}\label{fig:q3}Interaction of quarters
and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-23-1.pdf}
\caption{\label{fig:unnamed-chunk-23}\label{fig:q4}Interaction of quarters
and treatment. Control group is japanese vessels.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-24-1.pdf}
\caption{\label{fig:unnamed-chunk-24}\label{fig:ym1}Interaction of
year-month and treatment. Control group is all vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
\caption{\label{fig:unnamed-chunk-25}\label{fig:ym2}Interaction of
year-month and treatment. Control group is vessels from PNA.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-26-1.pdf}
\caption{\label{fig:unnamed-chunk-26}\label{fig:ym3}Interaction of
year-month and treatment. Control group excludes Chinese vessels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-27-1.pdf}
\caption{\label{fig:unnamed-chunk-27}\label{fig:ym4}Interaction of
year-month and treatment. Control group is japanese vessels.}
\end{figure}

\hypertarget{fishing-raster}{%
\subsubsection{Fishing raster}\label{fishing-raster}}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-28-1.pdf}
\caption{\label{fig:unnamed-chunk-28}\label{fig:fishing_raster_full}}
\end{figure}

### 2018-10-20 rmd/Manuscript.Rmd
Slight changes to manuscript, major results coming

Recall that to evaluate the redistribution of fishing effort we only track fishing vessels that belong to the treated group. In this case, we calculate the proportion of fishing effort allocated every month to each spatially explicit region outlined by EEZs and the high seas. For purse seiners, these represent 9 main EEZs, PIPA, the high seas, and a group of other EEZs. Figure \ref{fig:redist_trend_ps} shows the monthly relative fishing hours that each region received by all `r pipa_vessels` treated vessels. The top-left panel shows the change in fishing effort inside PIPA, including the preemptive fishing and immediate reduction previously reported \citep{mcdermott_2018}.

The change in the relative allocation of fishing effort by purse seiners increases in eight of the 12 regions after PIPA implementation (Table \ref{tab:disp_mod}). The largest increase is observed for the I-Kiribati EEZ, with an average increase of 0.11 (*p < 0.001*). In other words, the redistribution of treated vessels caused a 10\% increase in the *relative* allocation of fishing effort within I-Kiribati waters. The only decrease is observed for Papua New Guinea, but the coefficient is not significant. Figure \ref{fig:map_change_ps} provides a spatial representation of these changes. It is evident that the increase in relative fishing effort is greater for for regions closer to PIPA.

```{r, fig.width = 6, fig.height = 9}
mpas_WCPO <- mpas %>% 
  filter(wdpaid %in% c(309888, 400011))

@@

ggplot() +
  geom_raster(data = fishing_raster, mapping = aes(x = lon, y = lat, fill = hours_norm)) +
  geom_sf(data = eez, fill = "transparent", color = "black") +
  geom_sf(data = mpas_WCPO, fill = "transparent", color = "red") +
  # geom_sf(data = small_coast, color = "black") +
  # scale_fill_gradientn(colours = colorRamps::matlab.like2(50), trans = "log10") +
  scale_fill_viridis_c(trans = "log10") +
  facet_grid(year~treated, switch = "y") +
  # coord_equal() +
  ggtheme_map() +
  theme(legend.position = "bottom")
```

@@

```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for purse seiners."}

HS_disp_poly <- matrix(c(200, 10, 210, 10 ,210 ,20 ,200 ,20 ,200, 10),
                  ncol=2,
                  byrow=TRUE) %>%
  list() %>%
  st_polygon() %>% 
  st_sfc(crs = "+proj=longlat +datum=WGS84 +no_defs")

@@

commarobust::commarobust_tidy(disp_mod_ps1) %>% 
  mutate(b = str_detect(term, "Intercept"),
         c = str_detect(term, "post"),
         d = str_detect(term, "sate"),
         a = b*c,
         p1 = ifelse(p < 0.1, "*", ""),
         p2 = ifelse(p < 0.05, "*", ""),
         p3 = ifelse(p < 0.01, "*", ""),
    h_prop = paste0(formatC(est, digits = 3, format = "f"),
                    " (",
                    formatC(se, digits = 3, format = "f"),
                    ")",
                    p1,
                    p2,
                    p3)) %>% 
  filter(b+c+d > 0) %>% 
  select(term, h_prop) %>% 
  knitr::kable(booktabs = T,
               caption = "Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")

@@

>>>>

Recall that to evaluate the redistribution of fishing effort we only track fishing vessels that belong to the treated group. Figure \ref{fig:fishing_raster} provides a spatial representation of these changes. Note that 2013 effort distribution is roughly similar across vessels. Then in 2014 there is a sharp increase in fishing hours by treated vessels inside PIPA (blue paradox). In 2015 treated vessels then allocate more effort to the easternmost Kiribati EEZ (see Figure \label{fig:PNA_map}) and the high seas. In 2016 spatial distribution of fishing effort is again similar across groups. It is evident that the increase in relative fishing effort is greater for for regions closer to PIPA, and.

Four our empirical identification we calculated the proportion of fishing effort allocated every month to each spatially explicit regions defined in section \ref{methods}. For purse seiners, these represent 9 main EEZs, PIPA, the high seas, and a group of other EEZs. Figure \ref{fig:redist_trend_ps} shows the monthly relative fishing hours that each region received by all `r pipa_vessels` treated vessels. The top-left panel shows the change in fishing effort inside PIPA, including the preemptive fishing and immediate reduction previously reported \citep{mcdermott_2018}. The change in the relative allocation of fishing effort by purse seiners increases in eight of the 12 regions after PIPA implementation (Table \ref{tab:disp_mod}, fig:map_change_ps). The largest increase is observed for the I-Kiribati EEZ, with an average increase of 0.11 (*p < 0.001*). In other words, the redistribution of treated vessels caused a 10\% increase in the *relative* allocation of fishing effort within I-Kiribati waters. The only decrease is observed for Papua New Guinea, but the coefficient is not significant.

```{r, fig.width = 7.5, fig.height = 9, fig.cap = "\\label{fig:fishing_raster}Yearly spatial distribution of fishing effort by treated and control vessels. Colors have been adjusted relative to the maximum observed by group and year. "}
mpas_WCPO <- mpas %>% 
  filter(wdpaid %in% c(309888, 400011))

@@

fishing_raster %>% 
  filter(between(year, 2013, 2016)) %>% 
  ggplot() +
  geom_raster(mapping = aes(x = lon, y = lat, fill = hours_norm)) +
  geom_sf(data = eez, fill = "transparent", color = "black") +
  geom_sf(data = mpas_WCPO, fill = "transparent", color = "red") +
  # geom_sf(data = small_coast, color = "black") +
  # scale_fill_gradientn(colours = colorRamps::matlab.like2(50), trans = "log10") +
  scale_fill_viridis_c(trans = "log10") +
  facet_grid(year~treated, switch = "y") +
  # coord_equal() +
  ggtheme_map() +
  theme(legend.position = "bottom")
```

@@

```{r, fig.cap = "\\label{fig:map_change_ps}Spatial representation of the mean change in the monthly allocation of fishing effort for purse seiners."}
HS_disp_poly <- matrix(c(200, 10, 210, 10 ,210 ,20 ,200 ,20 ,200, 10),
                  ncol=2,
                  byrow=TRUE) %>%
  list() %>%
  st_polygon() %>% 
  st_sfc(crs = "+proj=longlat +datum=WGS84 +no_defs")

@@

commarobust::commarobust_tidy(disp_mod_ps1) %>% 
  mutate(b = str_detect(term, "Intercept"),
         c = str_detect(term, "post"),
         d = str_detect(term, "sate"),
         a = b*c,
         p1 = ifelse(p < 0.1, "*", ""),
         p2 = ifelse(p < 0.05, "*", ""),
         p3 = ifelse(p < 0.01, "*", ""),
    h_prop = paste0(formatC(est, digits = 3, format = "f"),
                    " (",
                    formatC(se, digits = 3, format = "f"),
                    ")",
                    p1,
                    p2,
                    p3)) %>% 
  filter(b+c+d > 0) %>% 
  select(term, h_prop) %>% 
  knitr::kable(booktabs = T,
               caption = "\\label{tab:disp_mod}Change in the relative allocation of purse seining fishing hours by region (R2 = 0.36, F(47, 69000) = 961.1, p < 0.001)") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position")

@@

### Fishing raster

```{r, fig.width = 7, fig.height = 10.5, fig.cap = "\\label{fig:fishing_raster_full}"}
ggplot() +
  geom_raster(data = fishing_raster, mapping = aes(x = lon, y = lat, fill = hours_norm)) +
  geom_sf(data = eez, fill = "transparent", color = "black") +
  geom_sf(data = mpas_WCPO, fill = "transparent", color = "red") +
  geom_sf(data = small_coast, color = "black") +
  # scale_fill_gradientn(colours = colorRamps::matlab.like2(50), trans = "log10") +
  scale_fill_viridis_c(trans = "log10") +
  facet_grid(year~treated, switch = "y") +
  # coord_equal() +
  ggtheme_map() +
  theme(legend.position = "bottom")
```
